\section {Notes}

\begin{enumerate}[label=(\roman*)]
\item Section 21.1 describes the operations supported by a disjoint-set data
  structure.
\item Section 21.2 describes the linked-list implementation for disjoint sets.
\item Section 21.3 presents a more efficient representation using rooted trees.
\item Section 21.4 analysis of union by rank with path compression.
\end{enumerate}

\section {Disjoint-set operations}

\textbf{MAKE-SET}($x$) creates a new set whose only member is $x$. Since the
sets are disjoint, we require that $x$ not already be in some other set.

\textbf{UNION}($x, y$) unites the dynamic sets that contain $x$ and $y$, say
$S_x$ and $S_y$, into a new set that is the union of these two sets.

\textbf{FIND-SET}($x$) returns a pointer to the representative of the (unique)
set containing $x$.

\subsection {An application of disjoint-set data structure}

The procedure CONNECTED-COMPONENTS that follows uses the disjoint-set operations
to compute the connected components of a graph. Once CONNECTED-COMPONENTS has
preprocessed the graph, the procedure SAME-COMPONENT answers queries about
whether two vertices are in the same connected component.

\textbf{CONNECTED-COMPONENTS($G$)}\\
1\hspace*{2ex} \textbf{for} each vertex $v \in G.V$\\
2\hspace*{4ex} MAKE-SET($v$)\\
3\hspace*{2ex} \textbf{for} each edge $(u, v) \in G.E$\\
4\hspace*{4ex} \textbf{if} FIND-SET$(u) \neq$ FIND-SET($v$)\\
5\hspace*{6ex} UNION($u, v$)

\textbf{SAME-COMPONENT($u, v$)}\\
1\hspace*{2ex} \textbf{if} FIND-SET($u$) $==$ FIND-SET($v$)\\
2\hspace*{4ex} \textbf{return} TRUE\\
3\hspace*{2ex} \textbf{else return} FALSE

\subsection {Exercises}

\subsubsection {21.1-1}

Suppose that CONNECTED-COMPONENTS is run on the undirected graph $G = (V, E)$,
where $V = { a, b, c, d, e, f, g, h, i, j, k }$ and the edges of $E$ are
processed in the order $(d, i), (f, k), (g, i), (b, g), (a, h), (i, j), (d, k),$
$(b, j), (d, f), (g, j), (a, e)$. List the vertices in each connected component
after each iteration of lines3-5.

\textbf{Solution}

\begin{tabular}{l|l}
Edge processed & Collection of disjoint sets \\
\hline
initial sets   & \{a\} \{b\} \{c\} \{d\} \{e\} \{f\} \{g\} \{h\} \{i\} \{j\} \{k\} \\
(d, i)         & \{a\} \{b\} \{c\} \{d, i\} \{e\} \{f\} \{g\} \{h\} \{j\} \{k\} \\
(f, k)         & \{a\} \{b\} \{c\} \{d, i\} \{e\} \{f, k\} \{g\} \{h\} \{j\} \\
(g, i)         & \{a\} \{b\} \{c\} \{d, i, g\} \{e\} \{f, k\} \{h\} \{j\} \\
(b, g)         & \{a\} \{b, d, g, i\} \{c\} \{e\} \{f, k\} \{h\} \{j\} \\
(a, h)         & \{a, h\} \{b, d, g, i\} \{c\} \{e\} \{f, k\} \{j\} \\
(i, j)         & \{a, h\} \{b, d, g, i, j\} \{c\} \{e\} \{f, k\} \{j\} \\
(d, k)         & \{a, h\} \{b, d, f, g, i, j, k\} \{c\} \{e\} \{j\} \\
(b, j)         & \{a, h\} \{b, d, f, g, i, j, k\} \{c\} \{e\} \{j\} \\
(d, f)         & \{a, h\} \{b, d, f, g, i, j, k\} \{c\} \{e\} \{j\} \\
(g, j)         & \{a, h\} \{b, d, f, g, i, j, k\} \{c\} \{e\} \{j\} \\
(a, e)         & \{a, e, h\} \{b, d, f, g, i, j, k\} \{c\} \{j\} \\
\end{tabular}

\subsubsection {21.1-2}

Show that after all edges are processed by CONNECTED-COMPONENTS, two vertices
are in the same connected component \textbf{if and only if} they are in the same
set.

\textbf{Solution}

If two vertices are in the same connected component, there must be some edges
that connect the two vertices, so they must be in the same set.

If two vertices are in the same set, there must be some edges that connect the
two vertices, so they must be in the same connected component.

\subsubsection {21.1-3}

During the execution of CONNECTED-COMPONENTS on an undirected graph $G = (V, E)$
with $k$ connected components, how many times is FIND-SET called? How many times
is UNION called? Express your answers in terms of $|V|, |E|$, and $k$.

\textbf{Solution}

FIND-SET: $|E| * 2$\\
UNION   : $|V| - k$

\subsection {My Implementation}

Let $A$ be the array that contains the minimum value of the set. For example,
$A[6] = 3$ indicates that the minimum value of the set, which $6$ belongs to, is
$3$. We will call the minimum value of the set as \textbf{ID}.

Let $S$ be the array that contains the value of each set. For example,
$S[3]=3, 6$ indicates that the set, whose ID is $3$, contains $3$ and the set
whose ID is $6$.

\textbf{FIND-SET($x$)}\\
1\hspace*{2ex} \textbf{return} $A[x]$\\

\textbf{UNION($x, y$)}\\
1\hspace*{2ex} $a = FIND-SET(x)$\\
2\hspace*{2ex} $b = FIND-SET(y)$\\
3\hspace*{2ex} \textbf{if} $a > b$\\
4\hspace*{4ex} $swap(a, b), swap(x, y)$\\
5\hspace*{2ex} \textbf{for} v in $S[b]$\\
6\hspace*{4ex} $A[v] = a$\\
7\hspace*{2ex} $S[a].append(b)$

Time Complexity: $O(NlgN)$\\
Space Complexity: $O(N)$


